\documentclass{article} % For LaTeX2e
\usepackage{midterm,times}
\usepackage{hyperref}
\usepackage{url}
%\documentstyle[nips13submit_09,times,art10]{article} % For LaTeX 2.09


\title{A Machine Learning Approach For E-sports Analysis}


\author{
Xiao Bo Zhao\\
Carnegie Mellon University\\
Pittsburgh, PA 15213 \\
\texttt{xiaoboz@andrew.cmu.edu} \\
\And
Shen Wang\\
Carnegie Mellon University\\
Pittsburgh, PA 15213 \\
\texttt{shenw@andrew.cmu.edu} \\
}

% The \author macro works with any number of authors. There are two commands
% used to separate the names and addresses of multiple authors: \And and \AND.
%
% Using \And between authors leaves it to \LaTeX{} to determine where to break
% the lines. Using \AND forces a linebreak at that point. So, if \LaTeX{}
% puts 3 of 4 authors names on the first line, and the last on the second
% line, try using \AND instead of \And before the third author name.

\newcommand{\fix}{\marginpar{FIX}}
\newcommand{\new}{\marginpar{NEW}}

\nipsfinalcopy % Uncomment for camera-ready version

\begin{document}


\maketitle

\begin{abstract}
In recent years, e-sport has gained its popularity, but the study of it has been lagged behind. Therefore, in this project, we look deep into the nature of e-sport and create models that can best predict its outcome. We look at the well studied models targeting the traditional sports and evaluate our approach against the existing models.
\end{abstract}

%---------------------------------------------------------
\section{Introduction}
In the last couple of years, e-sport saw a significant growth, both in terms of players and spectators \cite{Witkowski:2013:ERC:2513002.2513008}. Unlike traditional sports, online matches are formed quickly. Players can find and play against opponents within minutes. As a result, e-sport competitive play occurs very frequently. This fluidity also causes e-sports’ structure to differ significantly from traditional sports. To allow for fast paced match making in games like League of Legends, both teammates and opponents are chosen randomly from a large pool of players of similar ranking. Players on the same team most likely do not have prior collaboration history, while players facing against each other most likely have not studied each other’s strategies. Because of this added complexity, many well-studied models that predict traditional sports’ outcomes might no longer apply to e-sports. Therefore, in this study, we intend to develop a classifier adapted for e-sports’ structure, and in particular, for League of Legend’s competitive gaming model.\\
League of Legends is a multiplayer online battle arena game. The focus of it is to pitch two teams of 5 players into a gladiatorial type match. Each player plays as a champion, which is a character with a unique set of abilities. This choice directly defines the play style of each player. This game requires both high independent skill and teamwork to succeed. As a result, one match resembles the model of conventional team-based sports such as football and basketball.\\
One of the main differences between League of Legends and traditional sports is the role selection process. In traditional sports, a player's position and skills is determined outside of the game. However, in League of Legends, each player's champion is selected during a process called champion selection. This process is carried out at the beginning of the game, and once decisions are made, players are locked into their champion for the remaining of the game. No player or champion substitution is allowed during a game. As a result, champion selection is a crucial and often the most strategical part of the game.\\
League of Legends offer two main type of champion selection: blind pick and draft. In blind pick, players from both teams choose their champions simultaneously, and players from one team does not have knowledge of champions the opposing team is choosing. This mode provides a more laid-back game style and is played by casual players. In draft mode, players select champions based on a predetermined order. The pick order alternates between the two teams until all players have selected their champion. Champions selected cannot be reselected. As a result, players not only know the champions the opposing team chose, but also can force the opponent to choose undesirable champions or team compositions. The results of this game mode counts towards an in-game ranking. Therefore, players are much more careful and serious when engaging in this type of game play.\\
Our research's focus is on the draft game mode. Our goal is to be able to determine the outcome of the game just from the information available during champion selection. This prediction not only allows players to wisely choose champions, but also allows players to expect particular results before the actual game starts, allowing them to make strategical choices that could lead to increased number of victories and improvements of their personal ranking.
%---------------------------------------------------------

\section{Related work}
Given the similarities between e-sports and traditional sports, we believe that it is beneficial to look at some well studied models targeting traditional sports and use them as our baseline. There are many related works of this field~\cite{Joseph2006544}\cite{Min2008551}, and each of them provide unique angles to the problem. One particularly interesting model aimed to predict the outcome of football matches proposed by {A. Joseph et al.} is constructed based on Bayesian networks~\cite{Joseph2006544}. In this model, a Bayesian network is constructed based on the presence of key players, their positions, home-field benefit and an estimation of the quality of the opposing team. As far as we are concerned, this model has several important points. First of all, due to the nature of football game organizations, there is not much data to consider. That said, a particular football player only has a limited career time and there are only limited amount of football games in a season. As a result, for each player, their performance data are very limited. The insufficiency of data suggests that it is inappropriate to build models based on each player's performance in the games. To solve this problem, the proposed model only consider the presence of some key players as well as whether their initial playing positions. The observation is that a player, with his professional skills, will contribute to the team in the game - as long as he plays in that game. Another important design in the proposed model is the asymmetry between two teams in a game. As described, the players in one team will be checked specifically by the model while the other team is only represented as a general quality score assigned by an "expert". This design makes it possible for the "expert" to drive the direction of prediction. The 
%---------------------------------------------------------

\section{Methods}
However, one of the main differences between League of Legends and traditional sports is the match making and role selection process. Unless conventional sports where each player excels at a specific task and position. In League of Legends champions define the position and task, and players excel at a particular set of champions. However, it is not uncommon for players to choose widely different champions between games. As a result, players' role in a game 
%---------------------------------------------------------

\section{Experiments}

A table:

\begin{table}[t]
\caption{Sample table title}
\label{sample-table}
\begin{center}
\begin{tabular}{ll}
\multicolumn{1}{c}{\bf PART}  &\multicolumn{1}{c}{\bf DESCRIPTION}
\\ \hline \\
Dendrite         &Input terminal \\
Axon             &Output terminal \\
Soma             &Cell body (contains cell nucleus) \\
\end{tabular}
\end{center}
\end{table}
%---------------------------------------------------------

\section{Conclusion}

vvv
%---------------------------------------------------------

\section{References}

\bibliographystyle{midterm}
\bibliography{midterm}

\end{document}